---
title: "Miscellaneous"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## RNA-seq analysis references
[Yalamanchili *et al.* 2017: RNA-seq analysis pipeline](https://chenh19.github.io/rotation2/refs/Yalamanchili_2017.pdf)

## Routine

**Load:**

```{r,eval=FALSE}
# load
setwd("./rotation2/")
library(workflowr)
```

**WorkflowR publish:**

```{r,eval=FALSE}
# workflowR publish
wflow_publish("analysis/*.Rmd")
```

**Cleanup:**

```{r,eval=FALSE}
# cleanup environment
rm(list = ls())
```

**Git commit and push:**

```{bash,eval=FALSE}
# git pull
#mkdir ./rotation2/ && cd ./rotation2/ && git init
#git pull git@github.com:chenh19/rotation2.git

# git push
cd ./rotation2/
#git remote add origin git@github.com:chenh19/rotation2.git
#git commit -a -m "update"
#git add --all
git push -u origin main
```


## Meetings

- Xuanyao one-on-one: ```Tue 1pm``` and ```Thur 1pm```
- Liu group meeting: ```Wed 1pm``` (Work-in-progress/Journal clubs)
- Joint lab meeting (Andy & Haky groups): ```Thurs 2pm``` (Work-in-progress/Journal clubs)
- Yang lab journal club: ```Mon 1pm```
- PBC serminar (Matthew & Xin & John groups): ```Fri 10:30am```
- Group lunch: ```Wed 12pm```


## Git SSH configuration

```{bash,eval=FALSE}
# check for existing keys
#ls -al ~/.ssh

# create a key if does not exist
ssh-keygen -t ed25519 -C "your_email@example.com"
# when asked "Enter a file in which to save the key," press Enter (default file location)
# input a passphrase (anything you can remember)

# add SSH key to ssh-agent-
eval `ssh-agent -s`
ssh-add ~/.ssh/id_ed25519

# get the key
cat ~/.ssh/id_ed25519.pub
# copy the output key, then navigate to Github account and add the ssh key
```

- Ref: [YouTube](https://youtu.be/YnSMYgIybFU)


## Canon printer configuration

```{bash, eval=FALSE}
# Canon Color ImageCLASS MF735Cdw driver for linux
cd ~/Downloads
wget -q -O linux-UFRII-drv-v550-us-00.tar.gz https://pdisp01.c-wss.com/gdl/WWUFORedirectTarget.do?id=MDEwMDAwOTIzNjEx&cmp=ABR&lang=EN && sleep 10 && 
tar -xf linux-UFRII-drv-v550-us-00.tar.gz && sleep 1 && rm linux-UFRII-drv-v550-us-00.tar.gz
sudo bash ./linux-UFRII-drv-v550-us/install.sh && sleep 1 && rm -rf ./linux-UFRII-drv-v550-us/
sudo apt-get update && sudo apt install -f -y && sudo apt-get autoremove -y && sudo apt-get clean
```

- Note: the private IP address is labeled on the printer.
- Ref: [Canon Support](https://www.usa.canon.com/internet/portal/us/home/support/details/printers/color-laser/color-imageclass-mf735cdw)


## Watering Ran's plant in N410

- [x] 6/13/22 10:30AM

