---
title: "Miscellaneous"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Routine

**Load:**

```{r,eval=FALSE}
# load
setwd("./Developing/rotation2/")
library(workflowr)
```

**WorkflowR publish:**

```{r,eval=FALSE}
# workflowR publish
wflow_publish("./analysis/*.Rmd")
```

**Cleanup:**

```{r,eval=FALSE}
# cleanup environment
rm(list = ls())
```

**Git commit and push:**

```{bash,eval=FALSE}
# git pull
#mkdir ./Developing/rotation2/
#cd ./Developing/rotation2/
#git init
#git remote add origin git@github.com:chenh19/rotation2.git
#git pull git@github.com:chenh19/rotation2.git

# git push
#cd ./Developing/rotation2/
git commit -a -m "update"
git add --all
git commit -a -m "update"
git push -u origin main
```

**Environment: [Kubuntu 22.04 LTS](https://kubuntu.org/); [Setup Shell Scripts](https://github.com/chenh19/MyWorkspace)**

## 2. Meetings

- Xuanyao one-on-one: ```Tue 1pm``` and ```Thur 1pm```
- Liu group meeting: ```Wed 1pm``` (Work-in-progress/Journal clubs)
- Joint lab meeting (Andy & Haky groups): ```Thur 2pm``` (Work-in-progress/Journal clubs)
- Yang lab journal club: ```Mon 1pm```
- PBC serminar (Matthew & Xin & John groups): ```Fri 10:30am```
- Group lunch: ```Wed 12pm```


## 3. Git SSH configuration

**Code:** [```git_ssh_config.sh```](https://raw.githubusercontent.com/chenh19/MyWorkspace/main/src/cfg/0_gitssh.sh)  

- Ref: [YouTube](https://youtu.be/YnSMYgIybFU)


## 4. Canon printer configuration

**Code:** [```canon_printer.sh```](https://raw.githubusercontent.com/chenh19/rotation2/main/code/0_prepare/canon_printer.sh)  

- Note: the private IP address is labeled on the printer.
- Ref: [Canon Support](https://www.usa.canon.com/internet/portal/us/home/support/details/printers/color-laser/color-imageclass-mf735cdw)


## 5. Watering Ran's plant

- [x] 6/13/22 10:30am
- [x] 6/15/22 9:00am
- [x] 6/20/22 8:00am
