---
title: "Project-2: SCEPTRE"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Understand SCEPTRE

### a. Read the paper

[Barry *et al.* 2021: SCEPTRE](https://chenh19.github.io/rotation2/refs/Barry_2021.pdf)

> *First, SCEPTRE fits a **negative binomial distribution** to measure the effect of a single gRNA on a given gene via Z-score. Then, the distribution of gRNAs to cells is randomly sampled to build a gRNA-specific null distribution, recomputing a negative binomial Z-score. A skew-t distribution is fit to compare the test Z-score and the null distribution, and a two-sided p-value is derived, allowing for significance tests of increased or decreased gene expression.*  

From [Morris *et al.* 2021: STING-Seq](https://chenh19.github.io/rotation2/refs/Morris_2020.pdf)

### b. Check the package

- [Katsevich-Lab/sceptre](https://github.com/Katsevich-Lab/sceptre)
- [Katsevich-Lab/sceptre-manuscript](https://github.com/Katsevich-Lab/sceptre-manuscript)

### c. Install the package

**Code:** [```sceptre.sh```](https://raw.githubusercontent.com/chenh19/rotation2/main/code/0_prepare/sceptre.sh)  

### d. run sceptre

- SCEPTRE [tutorial](https://katsevich-lab.github.io/sceptre/articles/using_sceptre_v2.html)
- SCEPTRE [functions](https://katsevich-lab.github.io/sceptre/reference/index.html)

```{r,eval=FALSE}
Expression <- readRDS("../Morris_2021/filter/Expression.rds", refhook = NULL)
gRNA <- readRDS("../Morris_2021/filter/gRNA.rds", refhook = NULL)

gene_matrix <- Expression@assays$RNA@counts
gRNA_matrix <- gRNA@assays$RNA@counts

```

```{r,eval=FALSE}
#install.packages("devtools")
#devtools::install_github("katsevich-lab/sceptre")
#install.packages("tidyverse")
#install.packages("cowplot")

library(tidyverse)
library(cowplot)
library(Matrix)
library(sceptre)
```